\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}

\title{Math 210 (Modern Algebra I), Final Exam: Part 2, \\ {\normalsize Fall 2025; Instructor: Sam Hopkins; Taken on: Wednesday, December 3rd}}
\date{}

\begin{document}

\maketitle

This is the in-person part of the final, which you have 80 minutes to do. Partial credit will be given generously, so write as much as you know for each problem. Each problem is worth 10 points. 

\thispagestyle{empty}
\begin{enumerate}

\item \begin{enumerate}
\item Consider the permutation $\sigma = (1,2,3,4,5,6) \in S_6$, i.e., a six-cycle in the symmetric group on six letters. Write down the cycle notation of $\sigma^{i}$ for $i=0,1,\ldots,5$.
\item For general $n \geq 1$, if $\sigma \in S_n$ is an $n$-cycle, for which $i=0,1,\ldots,n-1$ will we have that~$\sigma^{i}$ is also an $n$-cycle? Explain.
\end{enumerate}

\item \begin{enumerate}
\item How many Sylow $2$-subgroups of the symmetric group $S_3$ are there? List them all.
\item How many Sylow $3$-subgroups of the symmetric group $S_3$ are there? List them all.
\item Verify that the subgroup counts you found in a) and b) agree with the Sylow theorems.
\end{enumerate}

\item For all of the following, explain why your examples work.
\begin{enumerate}
\item Give an example of a proper ideal of the integers $\mathbb{Z}$ which is \emph{not} a \emph{prime} ideal.
\item Give an example of a nonzero, proper ideal of the Gaussian integers $\mathbb{Z}[i]$ which \emph{is prime}.
\item Give an example of a proper ideal of the polynomial ring $\mathbb{Q}[x]$ over the rationals which is \emph{not prime}.
\item Give an example of an ideal of the polynomial ring $\mathbb{Z}[x]$ over the integers which is \emph{not} a \emph{principal} ideal.
\end{enumerate}

\item Give a specific example of a commutative ring $R$ and a short exact sequence of $R$-modules which is not split exact. Explain what this means, and why your example works.

\end{enumerate}


\end{document}
