\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}

\title{Howard Math 273, HW\# 3, \\ {\normalsize Fall 2021; Instructor: Sam Hopkins; Due: Friday, December 3rd}}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-1cm}

\begin{enumerate}

\item The \emph{complete bipartite graph $K_{n,m}$} is the graph with vertex set $X\cup Y$ where $X=\{x_1,...,x_n\}$ and $Y=\{y_1,...,y_m\}$, and with edges $\{x_i,y_j\}$ for all $1\leq i \leq n, 1\leq j \leq m$ (but with no edges between the $x$'s, or between the $y$'s). Use the Matrix-Tree Theorem to show that the number of spanning trees of $K_{n,m}$ is $n^{m-1}m^{n-1}$. \\
{\bf Hint}: you can use the fact that for a matrix in \emph{block form} $M=\begin{pmatrix} A & B \\ C & D \end{pmatrix}$ we have $\mathrm{det}(M) = \mathrm{det}(A-BD^{-1}C)\cdot\mathrm{det}(D)$ as long as $D$ is invertible (this generalizes $\mathrm{det}\begin{pmatrix} a & b \\ c & d\end{pmatrix}=ad-bc$).

\item  \emph{(Stanley, EC1, \#4.69)} Compute the number of closed walks of length $\ell$ in the complete bipartite graph $K_{n,m}$. Use this computation, together with the Transfer Matrix Method, to find the eigenvalues of the adjacency matrix of $K_{n,m}$.

\item \emph{(Stanley, EC1, \#3.34)} Recall that for a poset $P$, $\mathcal{J}(P)$ denotes the set of \emph{order ideals} of $P$ (i.e., subsets $I\subseteq P$ for which $q\in I$ and $p\leq q\in P$ implies $p\in I$). Find {\bf all} finite posets $P$ for which
\[ \sum_{I \in \mathcal{J}(P)} x^{\#I} = (1+x)(1+x^2)(1+x+x^2).\]
{\bf Hint}: How many order ideals must such a $P$ have? How many elements must $P$ have? How many \emph{minimal} elements must it have? How many \emph{maximal} elements must it have?

\item Let $P$ be a finite poset. An \emph{antichain} $A$ of $P$ is a subset $A\subseteq P$ of pairwise incomparable elements (i.e., for all $p,q\in A$, we have neither $p\leq q$ nor $q \leq p$). Let $\mathcal{A}(P)$ denote the set of antichains of $P$. Define a partial order $\preceq$ on $\mathcal{A}(P)$ by $A \preceq A'$ iff for every $p \in A$ there is some $p'\in A'$ with $p \leq p'$. Show that $(\mathcal{A}(P),\preceq)$ is isomorphic to $(\mathcal{J}(P),\subseteq)$, the distributive lattice of order ideals of $P$ under inclusion.

\item \emph{(Stanley, EC1, \#3.89)} Let $L$ be a finite lattice, with minimum element $\hat{0}$. Let $f_L(m)$ be the number of $m$-tuples $(t_1,\ldots,t_m)\in L^m$ such that $t_1 \wedge t_2 \wedge \cdots \wedge t_m = \hat{0}$. Use M\"{o}bius inversion to show that
\[ f_L(m) = \sum_{t\in L} \mu(\hat{0},t) \cdot (\#\{s\in L\colon s \geq t\})^m,\]
where $\mu$ is the M\"{o}bius function of $L$. \\
{\bf Hint}: Define $f_L(m,t) := \#\{(t_1,\ldots,t_m)\in L^m\colon t_1 \wedge t_2 \wedge \cdots \wedge t_m = t\}$ for any $t \in L$ (so that $f_L(m)=f_L(m,\hat{0})$), and also define $g_L(m,t) := \#\{(t_1,\ldots,t_m)\in L^m\colon t_1 \wedge t_2 \wedge \cdots \wedge t_m \geq t\}$. How are these $f$ and $g$ related? Can you find a simpler expression for $g$?

\end{enumerate}


\end{document}
