\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Midterm \#3, 11/25 \\ Math 156 (Calculus I), Fall 2024}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-1cm}

Each problem is worth 10 points, for a total of 50 points. You have 50 minutes to do the exam. Remember to \emph{show your work} on all problems!

\begin{enumerate}
\item For each of the following functions $f(x)$, write the most general anti-derivative $F(x)$ of $f(x)$.
\begin{enumerate}
\item $f(x)=2x^3 -3x^2+5x-7$
\item $f(x) = 4e^x - 2\sin(x)$
\item $f(x) = \displaystyle \sqrt{x} + \frac{1}{x^2}$
\item $f(x) = \displaystyle \frac{3}{x}-\cos(x)$
\end{enumerate}
\item Evaluate the following definite integrals using the Fundamental Theorem of Calculus. Write your answers in as simplified a form as you can.
\begin{enumerate}
\item $\displaystyle \int_{-1}^{5} x^2+x+1 \; dx$
\item $\displaystyle \int_{0}^{\pi/2} 2\cos(x) \; dx$
\item $\displaystyle \int_{0}^{\ln(2)} e^x - 1 \; dx$
\end{enumerate}
\item Approximate the area under the curve $y=x^2+x+1$ from $x=-1$ to $x=5$ by using $n=3$ rectangles (of equal width), with the sample points being the sub-intervals' {\bf left} endpoints. Is your approximation an over- or under-estimate of the true area?
\item The velocity (in meters per second) at time $t$ (in seconds) of a car moving along a one-dimesional road is given by the function $v(t)=2t+1$. What distance does the car travel between time $t=2$ seconds and time $t=5$ seconds?
\item Evaluate the following indefinite integrals using the $u$-substitution technique.
\begin{enumerate}
\item $\displaystyle \int 2x \cdot e^{3x^2+5} \; dx$
\item $\displaystyle \int \sqrt[3]{4x-2} \; dx$
\item $\displaystyle \int \frac{\cos(x)}{\sin(x)} \; dx$ \hfill [{\bf Hint}: let $u=\sin(x)$]
\end{enumerate}
\end{enumerate}

\end{document}