\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Quiz \#2, 9/6 \\ Math 156 (Calculus I), Fall 2022}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-1cm}

Problem 1 is worth 9 points (3 pts each part), and you get 1 point for free, for a total of 10 points. Remember to \emph{show your work} on all problems!

\begin{enumerate}
\item The following questions are about ``real world'' interpretations of ways to combine old functions together to form new functions (like $f+g, fg, f \circ g$, et cetera).
\begin{enumerate}
\item The cost of buying $x$ students each a sandwich is given by the function $f(x) = 5x$. The cost of buying $x$ students each a juice box is given by $g(x)= 2x$. What function represents the cost of buying $x$ students each a sandwich and a juice box? Explain.
\item Suppose that the total number of people employed in some small country's economy $x$ months from today is given by the function $f(x) = 50,000 + 500x$. Also, $x$ months from today, the average wage for a worker in that economy is given by $g(x) = 10,000 + 50x$. What function represents the total wages earned (i.e., by \emph{all} workers) in that economy $x$ months from today? Explain.
\item The amount of money (in dollars) you have after buying $x$ candy bars is given by the function $f(x) = 100 - 2x$. If you put $x$ dollars in a bank account, then the amount of money you will have after a year is given by the function $g(x) = 1.02x$ (because of interest). What functions represents the amount of money you have after a year if you buy $x$ candy bars and then put your remaining money in a bank account? Explain.
\end{enumerate}

\end{enumerate}

\end{document}