\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Midterm \#1, 2/25 \\ Math 157 (Calculus II), Spring 2025}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-1cm}

Each problem is worth 10 points, for a total of 50 points. You have 50 minutes to do the exam. Remember to \emph{show your work} on all problems!

\begin{enumerate}
\item Let $R$ be the region under the curve $y=x^2$ from $x=1$ to $x=2$. \begin{enumerate}
\item Compute the volume of the solid obtained by rotating $R$ about the $x$-axis.
\item Compute the volume of the solid obtained by rotating $R$ about the $y$-axis.
\end{enumerate}

\item Hooke's Law says that the force needed to maintain a spring stretched a distance $x$ beyond its resting position is $f(x) = \kappa x$, where $\kappa$ is the spring constant. 

Suppose that your spring has a spring constant of $\kappa = 10 \, N/m$ (newtons per meter). What is the work done stretching the spring $2.5$ meters beyond its resting position?

\item Compute the indefinite integral $\displaystyle \int (2x^2-3x+4) \, e^{x} \; dx$. ({\bf Hint}: try integration by parts.)

\item Compute the definite integral $\displaystyle \int_{0}^{3} \frac{1}{9+x^2} \; dx$. ({\bf Hint}: try a trigonometric substitution.) \\ Express your answer in the simplest form you can.

\item Compute the indefinite integral $\displaystyle \int \frac{2x-1}{x^2-9} \; dx$. ({\bf Hint}: try partial fractions.)

\end{enumerate}

\end{document}