\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Midterm \#3, 4/25 \\ Math 157 (Calculus II), Spring 2024}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-2cm}

Each problem is worth 10 points, for a total of 50 points. You have 50 minutes to do the exam. Remember to \emph{show your work} on all problems!

\begin{enumerate}

\item For each of the following sequence limits, state the value of the limit or state that it diverges. Explain your answer.
\begin{enumerate}
\item $\displaystyle \lim_{n\to \infty} \frac{5n^2-2n+6}{3n^2+2n+1}$
\item $\displaystyle \lim_{n\to \infty} \cos(\frac{2\pi}{n})$
\item $\displaystyle \lim_{n\to \infty} (-1)^n \cdot \frac{n}{n+1}$
\item $\displaystyle \lim_{n\to \infty} \sqrt{n}$
\end{enumerate}

\item For each of the following series, decide (with explanation) whether it converges or diverges.
\begin{enumerate}
\item $\displaystyle \sum_{n=1}^{\infty} \frac{n}{5n-1}$ \hfill ({\bf Hint}: check the limit of the terms.)
\item $\displaystyle \sum_{n=1}^{\infty} \frac{3}{5n-1}$ \hfill ({\bf Hint:} compare to a series you know.)
\item $\displaystyle \sum_{n=1}^{\infty} \frac{(-1)^{n-1}}{n+1}$ \hfill ({\bf Hint:} it is an alternating series.)
\item $\displaystyle \sum_{n=1}^{\infty} \frac{2^n+n}{4^n-n}$ \hfill ({\bf Hint:} look at the ratio of successive terms.)
\end{enumerate}

\item Consider the series $s=\displaystyle \sum_{n=1}^{\infty} \frac{1}{(2n+1)^2}$. Let $s_n = \frac{1}{3^2} + \frac{1}{5^2} + \cdots + \frac{1}{(2n+1)^2}$ be its $n$th partial sum.
\begin{enumerate}
\item Compute the second partial sum $s_2$ as an estimate for the true value $s$ of the series. \\ (Do not worry about simplifying your answer.)
\item Let $R_2 = s - s_2$ be the corresponding remainder, i.e., the error of your estimate from part (a). Give an upper bound for $R_2$. ({\bf Hint}: use an improper integral as the bound.)
\end{enumerate}

\item Consider the function $\displaystyle f(x) = e^{-2x}$.
\begin{enumerate}
\item Express this function as a power series centered at zero: $f(x) = \sum_{n = 0}^{\infty} c_n x^n$.
\item Determine the radius of convergence $R$ of the power series you found in part (a).
\end{enumerate}

\item Let $f\colon \mathbb{R}\to \mathbb{R}$ be a twice-differentiable function satisfying $f(0) = 3$, $f'(0) = 2$, and $f''(0)=1$.
\begin{enumerate}
\item Write the degree two Taylor polynomial $T_2(x)$, centered at $x=0$, for $f(x)$.
\item Use your answer in part (a) to estimate the value of $f(2)$. (You do not need to give any bounds on the error of your estimate.) 
\end{enumerate}

\end{enumerate}

\end{document}