\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Midterm \#1, 10/5 \\Math 181 (Discrete Structures), Fall 2022}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-1cm}

Each problem is worth 10 points, for a total of 50 points. You have 50 minutes to do the exam. Remember to \emph{show your work} and \emph{explain your answers} on all problems! 

\begin{enumerate}
\item In this problem, let the universal set be $U = \{1,2,3,4,5\}$ and let $A=\{1,3,4\}, B=\{2,4\}$. Write the following sets:
\begin{enumerate}
\item $(A\cap B)^c$ \hfill (this is also written $\overline{A\cap B}$ in the book)
\item $B \setminus A$ \hfill (this is also written $B-A$ in the book)
\item $(A \setminus B) \cup (B \setminus A)$
\end{enumerate}
\item Write truth tables for $p \to q$ and $q \vee \neg p$. What does this tell you about the two propositions?
\item Convert this argument to a symbolic form, and determine (with explanation) if it is valid: \\[0.5em]
Hypotheses: If I woke up early, then I'll go for a run. I do not go for a run. \\
Conclusion: I did not wake up early.
\item Let $P(x)$ be the propositional formula ``$x^2 \geq 1$,'' where the domain of discourse is the set $\mathbb{R}$ of all real numbers. Write the proposition ``$\neg (\forall x \; P(x))$'' in English words, and determine (with explanation) if it is true or false.
\item Give a direct proof of the following theorem: ``The product of an even integer and any integer is an even integer.''
\end{enumerate}

\end{document}