\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Quiz \#4, Due: 9/21 \\Math 181 (Discrete Structures), Fall 2022}
\date{}

\begin{document}

\maketitle

\thispagestyle{empty}

\vspace{-1cm}

Problem 1 is worth 4 points ($1$ pt each part), Problem 2 is worth 4 points ($1$ pt each part),  and Problem 3 is worth 2 points, for a total of 10 points. Remember to \emph{show your work} and \emph{explain your answers} on all problems!

\begin{enumerate}
\item Let $P(x)$ denote the statement ``$x$ is a professional athlete'' and $Q(x)$ the statement ``$x$ plays soccer.'' The domain of discourse is the set of all people. For each of the following: write the proposition in English, and determine if it is true or false.
\begin{enumerate}
\item $\forall x \; Q(x) \to P(x)$
\item $\forall x \; P(x) \vee Q(x)$
\item $\exists x \; \neg P(x) \wedge Q(x)$
\item $\exists x \; P(x) \wedge \neg Q(x)$
\end{enumerate}

\item Let $P(x)$ denote the statement ``$x$ is a musician'' and $Q(x)$ the statement ``$x$ plays piano.'' The domain of discourse is the set of all people. For each of the following: write the proposition symbolically, and determine if it is true or false.
\begin{enumerate}
\item Every musician plays piano.
\item Everyone who plays piano is a musician.
\item Some musician plays piano.
\item Someone who plays piano is a musician.
\end{enumerate}

\item Write the saying ``Not all those who wander are lost'' symbolically as a quantified statement.

\end{enumerate}

\end{document}
