\documentclass[11pt]{article}
\usepackage[tmargin=0.5in,bmargin=1in,rmargin=1.5in,lmargin=1.5in]{geometry}
\geometry{letterpaper}

\usepackage{amsmath}

\usepackage{verbatim}

\title{Poker hand probabilities, \\ UMTYMP Advanced Topics, Fall 2020}
\date{}


\begin{document}



\maketitle

\thispagestyle{empty}

\vspace{-1cm}

In a standard deck of cards, there are 4 possible suits (clubs, diamonds, hearts, spades), and 13 possible values (2, 3, 4, 5, 6, 7, 8, 9, 10, Jack, Queen, King, Ace). Let A, J, Q, K represent Ace, Jack, Queen and King, respectively. Every card has a suit and value, and every combination is possible. Hence a standard deck contains $13 \cdot 4 = 52$ cards. A ``poker hand'' consists of $5$ unordered cards from a standard deck of $52$. There are $\binom{52}{5} = 2, 598, 960$ possible poker hands. Let us now calculate the probability of each of the standard kinds of poker hands.

{\bf Royal Flush.} This hand consists of values 10, J, Q, K, A, all of the same suit. There are $\rule{3cm}{0.15mm}$ royal flushes, for a probability of $0.000154\%$.

{\bf Straight Flush.} A straight flush consists of five cards with values in a row, all of the same suit. Ace may be considered as high or low, but not both. (For example, A, 2, 3, 4, 5 is a straight, and 10, J, Q, K, A is a straight, but Q, K, A, 2, 3 is not a straight.) Excluding the royal flushes we already counted, there are $\rule{3cm}{0.15mm}$ straight flushes, for a probability of $0.00139\%$.

{\bf Four of a Kind.} This hand consists of four cards of one value, and a fifth card of a different value. There are $\rule{3cm}{0.15mm}$ four of a kinds, for a probability of  $0.0240\%$.

{\bf Full House.} This hand consists of three cards of one value, and two cards of a different value. There are $\rule{3cm}{0.15mm}$ full houses, for a probability of $0.144\%$.

{\bf Flush.} A flush consists of five cards, all of the same suit, \emph{with not all values in a row} (to exclude the straight flushes we already counted). There are $\rule{3cm}{0.15mm}$ flushes, for a probability of $0.197\%$.

{\bf Straight.} A straight consists of five values in a row, \emph{not all of the same suit} (to exclude the straight flushes we already counted). There are $\rule{3cm}{0.15mm}$ straights, for a probability of $0.392\%$.

{\bf Three of a Kind.} This hand consists of three cards of one value, and two more cards, each of different values. There are $\rule{3cm}{0.15mm}$ three of a kinds, for a probability of $2.11\%$.

{\bf Two Pairs.} This hand consists of two pairs of different values, and a fifth card of another different value. There are $\rule{3cm}{0.15mm}$ three of a kinds, for a probability of $4.75\%$.

{\bf One Pair.} This hand consists of a pair of one value, and three additional cards, each of different values. There are $\rule{3cm}{0.15mm}$ pairs, for a probability of $42.3\%$.

{\bf Nothing.} This is any hand that does not fall into one of the above categories. There are $\rule{3cm}{0.15mm}$ nothings, for a probability of $50.1\%$.



\end{document}
